% Matt Mollison
% matt.mollison@gmail.com

\documentclass[12pt]{article}
\usepackage[letterpaper, margin=1.1in]{geometry} % showframe
\usepackage{wallpaper}

% don't hyphenate
% \hyphenpenalty=10000
% \raggedright

\begin{document}

\centering

% # add border and make background white for potrace
% convert hops_upper_left.png -background white -gravity center -extent 587x382 hops_upper_left_border.png
% convert hops_lower_right.png -background white -gravity center -extent 587x382 hops_lower_right_border.png

% # convert to pnm
% convert hops_upper_left_border.png hops_upper_left_border.pnm
% convert hops_lower_right_border.png hops_lower_right_border.pnm
% # smooth with potrace
% potrace -b pdf -i -o hops_upper_left_border.pdf hops_upper_left_border.pnm
% potrace -b pdf -i -o hops_lower_right_border.pdf hops_lower_right_border.pnm

\ULCornerWallPaper{.3}{./img/hops_upper_left_border.pdf}
\LRCornerWallPaper{.3}{./img/hops_lower_right_border.pdf}

% \textsc{{\LARGE Ceremony Program}
% \vspace*{\fill}

\textsc{\large Alice \& Matt: Wedding Script}
% \vspace*{\fill}
\vspace*{.2in}

% \textsc{\large Flagstaff Mountain Sunrise Amphitheater}
% % \vspace*{\fill}
% \vspace*{.01in}

\textsc{\large Boulder, CO}
% % \vspace*{\fill}
\vspace*{.01in}

\textsc{\large June 27, 2015}
% \vspace*{\fill}
\vspace*{.25in}

\section*{Things to to set up}

\begin{itemize}
\item Shelf w/ cloth and/or flowers on it
\item Chair
\item iPad with ceremony script, 2 hard copies of script in binders
\item Containers of beer stuff, candle in a jar, glass/jar to pour into, matches or lighter
\item Guitar, in its case
\item Microphone (backup)
\end{itemize}

\section*{Processional} (5-10 minutes)

\begin{enumerate}
\item {\it Fabian is playing guitar as everyone enters - stool for Fabian! Guitar stand, guitar case.}
\item {\it Paloma enters from the side and stands behind the table/altar thing}
\item {\it Matt enters with both of his parents}
\item {\it Bridesmaids and groom's crew walk arm in arm down the stage left stairs, go to their places to either side of the table}

  \begin{enumerate}
  \item Wade \& Molly S
  \item Anthony \& Kate
  \item Adam \& Sarah
  \item Dana, Lauren, and Molly
  \end{enumerate}

\item {\it Adeline and Eleanor walk down, twirling their ribbon stick thingies, then go sit with Jarrod in the front row}
\item {\it Alice enters with both of her parents}
  % \item {\it Have wedding party people stand up there the whole time, or sit down?}
\end{enumerate}

\newpage

\section*{Ceremony}

\begin{enumerate}
\item \textsc{Community Greeting} (3 minutes)
  \begin{itemize}
  \item {\bf Paloma}:  Welcome everybody from near and far. Matt and Alice  would not be here today without the support of their community  of family and friends---that's you! All of you are here today to give your love and support as part of the community that forms the foundation for a strong marriage. Matt and Alice want to thank you for joining us, and acknowledge those who couldn't be with us today but are also an integral part of that foundation. Please shake hands with the people around you, and give yourselves a pat on the back for all you've done to help them get where they are today. 
  \end{itemize}
\item \textsc{Welcome} (5 minutes, lengthiness optional)
  \begin{itemize}
  \item {\bf Paloma}:
    \begin{itemize}
    \item Marriage doesn't change anything.
    \item Matt and Alice are not starting their life together today. They have a life together. They have already grown together.
    \item They're building your own myths. They're creating stories together. And they're pooling their personal histories.
    \item They're going to continue to have experiences that turn into inside jokes, and extravagant outdoor cooking adventures and biking hither and yon will be the building blocks of stories and myths that make them who they are.
    \item This ceremony is about communicating their commitment to the world. It's a way to proclaim that they on the same team. And being on the same team, they're going to use their different skills to complement each other. It's about making the ride smoother for each other.
    \item This ceremony is also a way of looking at them today, the way they stand before their community, and getting ready for what's in store, and being excited for what they're going to do next.
    \end{itemize}
  \end{itemize}

\item \textsc{Reading 1}: {\bf Rich} (3 minutes)

  \begin{itemize}
  \item {\bf Paloma}: Now Alice's father, Rich, will read an excerpt from \underline{Corelli's Mandolin} by Louis de Berniere.

    \newpage

  \item {\bf Rich}:
    \begin{itemize}
    \item ``Love is a temporary madness. It erupts like an earthquake and then subsides. And when it subsides you have to make a decision. You have to work out whether your roots have become so entwined together that it is inconceivable that you should ever part. Because this is what love is. Love is not breathlessness, it is not excitement, it is not the promulgation of promises of eternal passion. That is just being ``in love'' which any of us can convince ourselves we are. Love itself is what is left over when being in love has burned away, and this is both an art and a fortunate accident. Your mother and I had it, we had roots that grew towards each other underground, and when all the pretty blossoms had fallen from our branches we found that we were one tree and not two.''
    \end{itemize}
  \end{itemize}

\item \textsc{Home brewing unity ceremony} (5-7 minutes)
  \begin{itemize}
  \item [] {\bf Paloma}: Now Alice and Matt's brothers, Paul and Wade, will lead a home brewing unity ceremony.
  
  \item [I.] \textsc{Introduction}
    {\bf Wade}: Matt and Alice love brewing beer as much as they love drinking it. From brewing beer together, they have learned to work as a team, to plan and solve problems together, to stick with a complicated task, and to see each beer through hours of brewing, weeks of fermenting, and years of aging. Matt and Alice  will apply the same qualities of perseverance, patience, and cooperation to both the obstacles and the joyful times that will fill the years to come.
    
  \item [II.] \textsc{Water}
    {\bf Paul}: Water is the foundation of life on earth, and the foundation of any beer, just as love is the foundation of Matt and Alice's relationship. Matt, Alice - please add water to the brewing vessel.
    \begin{itemize}
    \item \textit{(Matt and Alice each pour in a little water)}
    \end{itemize}

    
  \item [III.] \textsc{Barley}
    {\bf Wade}: To that water, you add barley, which provides the sugar that will feed the yeast. Barley gives sustenance, just as Matt and Alice sustain each other, not just with delicious meals, but by supporting each other in all aspects of life. Their deep bond is sustained by  this unconditional support in all things. Add the barley to the brewing vessel.
    \begin{itemize}
    \item \textit{(Matt and Alice each pour in a little barley)}
    \end{itemize}

  \item [IV.] \textsc{Fire}
    {\bf Paul}: The heat from a flame breaks down the sugars from the barley. Just as the pot sometimes boils over, Matt and Alice will encounter turbulent times in the future, but they will continue to learn and grow together, and from those experiences, a stronger bond will be formed. Light the candle and place the glass over the heat.
    \begin{itemize}
    \item \textit{(Matt \& Alice light a candle in a jar, wave the glass of water \& barley over the flame briefly, blow out the candle)}
    \end{itemize}

  \item [V.] \textsc{Hops}
    {\bf Wade}: Originally, hops were added to beer to preserve it, so that it could be stored for great lengths of time in cellars or on ships. In more recent years, brewers have also begun to use hops for their floral flavors and aromas. These hops represent Matt and Alice's commitment to preserving their marriage over a lifetime, through long winters and choppy seas, but they are also a reminder to stop and smell the flowers, to take the time each day to appreciate each other. Smell the hops, and then add them to the brewing vessel.
    \begin{itemize}
    \item \textit{(M \& A each smell and add some hops)}
    \end{itemize}

  \item [VI.] \textsc{Yeast}
    {\bf Paul}: In the final stage of the brewing process, yeast is added to the beer. This is the magic that turns sugar into alcohol, and turns wort into beer. Where before you had funky-smelling sugar water, after the yeast runs its course, you're left with  something tasty and intoxicating. When we talk about marriage, we often talk about the serious things, but Matt and Alice's relationship also relies on the joy and laughter they bring to each other. They will fill each other's days with merriment by never losing their love of fun and adventure. Last but not least, add the yeast to the brewing vessel.
    \begin{itemize}
    \item \textit{(M \& A each sprinkle some yeast)}
    \end{itemize}

    
  \item [VII.] \textsc{Time}
    {\bf Wade}: The final ingredient of brewing a beer is time. Matt and Alice are making a promise to spend the rest of their years together, knowing that their relationship will change, that they each will change as individuals, and that the world will change around them. Through it all, they will have each other. Matt and Alice, seal the jar.
    \begin{itemize}
    \item \textit{(Matt and Alice seal the jar together)}
    \end{itemize}
  \end{itemize}


\item \textsc{Reading 2}: {\bf Kate} (3 minutes)

  {\bf Paloma}: Now Matt's sister Kate will read an excerpt from the Massachusetts Supreme Judicial Court's ruling in the case of Goodridge \textit{vs.} the Department of Public Health, as well as yesterday's decision from the United States Supreme Court.

  \newpage

  \begin{itemize}
  \item {\bf Kate}:
    \begin{itemize}
    \item Marriage is a vital social institution. The exclusive commitment of two individuals to each other nurtures love and mutual support; it brings stability to our society. For those who choose to marry, and for their children, marriage provides an abundance of legal, financial, and social benefits. In return it imposes weighty legal, financial, and social obligations.

    \item Without question, civil marriage enhances the ``welfare of the community.'' It is a ``social institution of the highest importance.''

    \item Civil marriage is at once a deeply personal commitment to another human being and a highly public celebration of the ideals of mutuality, companionship, intimacy, fidelity, and family. Because it fulfills yearnings for security, safe haven, and connection that express our common humanity, civil marriage is an esteemed institution, and the decision whether and whom to marry is among life's momentous acts of self-definition.

    \item No union is more profound than marriage, for it embodies the highest ideals of love, fidelity, devotion, sacrifice, and family. In forming a marital union, two people become something greater than once they were.

    \end{itemize}

  \end{itemize}

\item \textsc{Expression of intent} (2 minutes)
  \begin{itemize}
  \item {\bf Paloma}: Now we've arrived at the heart of the ceremony, the part where Matt and Alice make some promises to each other, and you make some promises to them.

  \item {\bf Paloma}: Alice and Matt, do you freely and unreservedly offer yourselves to each other?

  \item {\bf A+M}: We do.

  \item {\bf Paloma}: Will you live together in faithfulness, joy, and mutual respect for the rest of your lives?

  \item {\bf A+M}: We will.

  \item {\bf Paloma}: Do you take each other to be your eternal partners in crime?

  \item {\bf A+M}: We do.

  \item {\bf Paloma}: \textit{(addressing audience)} Will all of you gathered uphold and honor Matt and Alice, and respect and celebrate their union? If so, say \textbf{``We will.''}

  \item \textit{All}: We will.

  \item \textbf{Paloma}: Will you stand by them in times of trouble, and celebrate with them in times of joy?

  \item \textit{All}: We will. 
  \end{itemize}

\item \textsc{Vows \& Ring exchange} (7 minutes)
  \begin{itemize}
  \item {\bf Paloma}: Matt and Alice will  now read the vows that they wrote for each other.

  \item {\bf Alice}:
    \begin{itemize}
    \item When I say you are the best, which we tell each other often, what I mean is: you are the best listener, you are the best thinker, you are the best friend, you are the hardest worker, you are the most compassionate, you are the best dog-dad, you are the best partner in all adventures, you are the kindest, you are the most thoughtful. I've never met anyone like you, and I can't believe I get to have you. 
  
    \item I promise to be there for you every day. I'll be there for you to come home to, to celebrate your successes and listen to your worries. On bad days, I'll be your partner in problem solving, if that's what you need, or I'll build you a blanket fort and cook you a pizza, if that's what you need. 

    \item I promise to communicate with you always, so that neither of us is ever left out of the other's thoughts. I will be honest and open with you, and I will be ready to listen to you openly. I will always communicate how much I appreciate the things you do for me, no matter how small. I will be president of the Matt Mollison appreciation society.

    \item I promise to hold onto this feeling forever, and remember every day the countless reasons I love you. If we fight, when we fight, we can pause and return to this moment, and find the strength in ourselves and each other to make it through anything.
\end{itemize}


  \item {\bf Matt}:
    \begin{itemize}
    \item You embody everything that I could hope to find in my best friend and partner in crime: Humor, opinion, a sense of compassion, creativity, and a distaste for fashion.

    \item Humor, I think, is foundational for any relationship. I promise to continue loving your face as we grow together and we develop laugh lines.

    \item I love your strong opinions and your wide array of knowledge. I promise to always have your back, and to cultivate these experiences so that our conversations will become even richer.

    \item We both have a deep sense of compassion for the world at large, as well as for each other when we encounter hurdles in our lives. I promise that you will always be able to find shelter somewhere in me, and I know that I will always find great comfort in you.

    \item Whether it's MacGyvering a brewing stir plate out of a Frisbee and a computer fan, or bushwhacking our own bike path through the fields of Belgium, I love the smile on your face as we experiment and create together. I promise to support you physically and emotionally as we pursue new creative paths.

    \item Your style, in my opinion, is at once tasteful and bright, resourceful and creative. I think you're the most beautiful woman in the world, and I promise to continue to love you as we ripen into old age.
    \end{itemize}

  \item {\bf Paloma}: Now it's time for you to seal the deal by giving each other rings. Think of these as magic rings that hold all the power of the promises and intentions in the vows you just said to each other. When you wear them, you are permanently encapsulated by love.

  \item \textit{Anthony will have the rings in his pocket - Anthony comes forward and gives Matt's ring to Alice.}

  \item {\bf Paloma}: Alice, repeat after me: \textbf{With this ring, I thee wed.}

  \item {\bf Alice}: With this ring, I thee wed \textit{(put ring on Matt!)}

  \item \textit{Anthony gives Alice's ring to Matt}

  \item {\bf Paloma}: Matt, repeat after me: \textbf{With this ring, I thee wed.}

  \item {\bf Matt}: With this ring, I thee wed \textit{(put ring on Alice!)}
  \end{itemize}

\item \textsc{Pronouncement and kiss}
  \begin{itemize}
  \item {\bf Paloma}: I now pronounce you husband and wife! You may kiss each other. 

  \item \textit{Matt \& Alice kiss!}

  \item \textit{Fabian plays guitar as wedding party leaves the stagey area} (5 minutes)

  \item \textit{Matt \& Alice leave together first - go get a quick picture taken, sign our marriage license, and spend a couple minutes alone}

  \item \textit{Wedding party leaves up the aisle in reverse order from how they arrived}

  \item \textit{Fabian and Paloma leave last}
  \end{itemize}
\end{enumerate}


\end{document}
